\section{Stimulus}%
%
\shortdef{That which is perceived or experienced (bodily, perceptually, or emotionally).}

\psst{Stimulus} does not seem to have any prototypical adposition 
in the languages we have looked at. In English, it can be construed in several ways:
\begin{exe}
  \ex My affection \p{for} you (\rf{Stimulus}{Beneficiary})
  \ex Scared \p{by} the bear (\rf{Stimulus}{Causer})
  %\ex We were listening \p{to} the music. (\rf{Stimulus}{Goal})
  \ex You should \choices{listen\\pay attention} \p{to} the music. (\rf{Stimulus}{Goal})
  \ex \rf{Stimulus}{Direction}:
    \begin{xlist}
      \ex We were looking \p{at} the photo.
      \ex\label{ex:AngryAt} I was angry \p{at} him. [cf.~\cref{ex:AngryWith}]
      \ex I startled \p{at} the noise.
    \end{xlist}
  \ex \rf{Stimulus}{Topic} is assigned to cases where the PP describes the topic or content of one's emotion: 
    \begin{xlist}
      \ex I care \p{about} you.
      \ex That's what I love \p{about} the show.
      \ex I took\_pride \p{in} the results.
      \ex I was \choices{proud \p{of}\\happy \p{with}} the results.
      \ex\label{ex:AngryWith} I was angry \p{with} him. [cf.~\cref{ex:AngryAt}]
      \ex\label{ex:InLoveWith} I was in$_{\text{\rf{Manner}{Locus}}}$ love \p{with} him. [cf.~\cref{ex:InLove}]
      \ex They bored me \p{with} their incessant talk about cats.
    \end{xlist}
  \ex\label{ex:StimBen} \rf{Stimulus}{Beneficiary}:
    \begin{xlist} % Also seems to be a metaphorical connection to Direction, but that would require multiple construal to express.
      \ex Her disdain \p{for} customers was apparent.
      \ex He has/feels compassion \choices{\p{towards}\\\p{for}} animals. % for TOWARDS multiple construal would be nice: Stimulus ~> Beneficiary ~> Direction
    \end{xlist}
  \ex I am \choices{thankful\\grateful} \p{for} your help. (\rf{Stimulus}{Explanation})
\end{exe}
See also: \psst{Topic}, \psst{Beneficiary}

Counterpart: \psst{Experiencer}

