\section{Theme}

\shortdef{Undergoer that is a semantically core participant in an event or state, 
and that does not meet the criteria for any other label.}

Prototypical \psst{Theme}s undergo (nonagentive\footnote{We distinguish agentivity at the token level, 
unlike VerbNet, where the subject of motion verbs like \emph{arrive} is \psst{Theme} because it need not be agentive.}) motion, are transferred, 
or undergo an internal change of state (sometimes called \emph{patients}).
Adpositional \psst{Theme}s are usually, but not always, construed as something else:
\begin{exe}
  \ex\begin{xlist}
    \ex Quit \p{with} the whining!
    \ex She helped me \p{with} my taxes.
    \ex Don't \choices{bother\\waste time} \p{with} an extra trip.
    \ex I managed to cope \p{with} \choices{the heavy load\\my fear of heights}.
  \end{xlist}
  \ex There's nothing wrong \p{with} the engine.
  \ex Fill the bowl \p{with} water. (\rf{Theme}{Instrument})
  \ex\begin{xlist}
      \ex The food was covered \p{with} grease. (\rf{Theme}{Instrument})
      \ex The food was covered \p{in} grease. (\rf{Theme}{Locus})
    \end{xlist}
  \ex My hovercraft is full \p{of} eels.
  %\ex I wouldn't want to deprive you \p{of} this opportunity. - Theme or Possession?
  \ex \begin{xlist}
      \ex\label{ex:search-for} Sheldukher \choices{looked\\searched\\fumbled} \p{for} his laser pistol.\\{}
      [contrast with transitive verb plus \psst{Characteristic} in \cref{ex:search-obj-for}]
      \ex Sheldukher \choices{asked\\made a request} \p{for} his laser pistol.
      \ex There is a significant demand \p{for} new housing.
      \ex Let's wait \p{for} \choices{Steve\\more information\\the end of the party}.
    \end{xlist}
  \ex The mechanic made a repair \p{to} the engine. (\rf{Theme}{Goal})
  \ex
  {\setlength\multicolsep{0pt}%
  \begin{multicols}{2}
    \begin{xlist}
        %\ex the price \p{of} tea % moved to Gestalt
        \sn \psst{Theme}
        \ex the approach \p{of} the waves
        \ex the \choices{death\\murder} \p{of} a salesman
        
        %\sn the tea\p{'s} price % moved to Gestalt
        \sn \rf{Theme}{Gestalt}
        \sn the wave\p{s'} approach
        \sn the salesman\p{'s} \choices{death\\murder}
    \end{xlist}
  \end{multicols}}
  \ex \begin{xlist}
      \ex The mechanic worked \p{on} the engine.
      \ex We noshed \p{on} snacks.
      \ex Students spend a lot of money \p{on} textbooks.
    \end{xlist}
  \ex \begin{xlist}
      \ex There was an increase \p{in} oil prices.
      \ex I'm covered \p{in} bees! (\rf{Theme}{Locus})
    \end{xlist}
  \ex \begin{xlist}
      \ex The training saved us \p{from} almost certain death. (\rf{Theme}{Source})
      \ex They prevented us \p{from} boarding the plane. (\rf{Theme}{Source})
    \end{xlist}
\end{exe}

\paragraph{Goods and services.}
In a commercial scene, the preposition introducing the item or event 
incurring a cost receives \psst{Theme} as its scene role. 
If the object of the preposition denotes an event and the preposition 
is \p{to}, \p{for}, or similar, then the construal \rf{Theme}{Purpose} is used:
\begin{exe}
  \ex \begin{xlist}
    \ex They spent \$500 \p{on} the repairs. (\psst{Theme})
    \ex They charged/paid/owed \$500 \p{for} the bicycle. (\psst{Theme})
    \ex They charged/paid/owed \$500 \p{for} the repairs. (\rf{Theme}{Purpose})
    \ex They asked \$500 \p{to} make the repairs. (\rf{Theme}{Purpose})
    \ex \$500 \choices{\p{for}\\\p{to} make} the repairs was excessive. (\rf{Theme}{Purpose})
  \end{xlist}
\end{exe}

\paragraph{\emph{Between} and \emph{among}.}
When two symmetric undergoers are collected in a single NP 
functioning as a set, it is marked as a \psst{Whole} construal:
\begin{exe}
  \ex There was a collision in mid-air \p{between} two light aircraft. (\rf{Theme}{Whole})
  \ex Links \p{between} science and industry are important. (\rf{Locus}{Whole})
\end{exe}

\begin{history}
  In v1, following many thematic role inventories, 
  \sst{Patient} was a distinct label for undergoers that were 
  affected (undergoing an internal change of state). 
  It was merged into \psst{Theme} for v2 because the affectedness criterion can be subtle 
  and difficult to apply.
\end{history}

Compare: \psst{Co-Theme}

See also: \psst{Beneficiary}

